\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Shorten.

\begin{wrapfigure}{r}{0.33\linewidth}
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwx) {$\rwx$};
    \node[main node] (rx) [below right of=rwx] {$\rx$};

@@

Any reasonable capability machine needs a way to set up boundaries between security domains as well as a way to cross the boundaries in a way where each domain retains their authority.
%The M-Machine~\citep{Dally1997Memo59} inspired capability machine in \citet{skorstengaard_reasoning_2017} uses enter-capabilities to achieve this.
On \trgcm{} we have sealed capabilities to achieve this.
Syntactically, sealed capabilities add two things to the capability machine: Sets of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$ and sealed capabilities $\sealed{\sigma,\vsc}$.
% seals
A set of seals consists of a range of available seals $[\sigma_\var{base},\sigma_\var{end}]$ and the current seal $\sigma$ which is represented by a natural number.
% sealed caps
A sealed capability consists of a sealable $\vsc$ and the seal $\sigma$ it has been sealed with.
The sealables are the sets of seals and the capabilities, and we refer to the set of them as $\SealableCaps$.
The system native tokens $\Cap$ on \trgcm{} are the sealables and the sealed capabilities.

%%% Domains
The words on \trgcm{} are the system native tokens in $\Cap$ and data which is represented by $\ints$.
We assume a finite set of register names $\RegName$ that at least contains register names $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$, and we define register files as functions from register names to words.
We have a notion of a complete memory where all memory addresses contains a word and a memory segment that need not contain words on all addresses.
Both are represented as functions from addresses, defined as the natural numbers, to words, but the memory segment functions only need to be partial.
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.\ an attempt to break the capability machine guarantees.
An executable configuration is a register file and memory pair.

>>>>

\begin{wrapfigure}{r}{0.28\linewidth}
  \centering
  \begin{tikzpicture}[main node/.style={}]
    \node[main node] (rwx) {$\rwx$};
    \node[main node] (rx) [below right of=rwx] {$\rx$};

@@

Any reasonable capability machine needs a way to set up boundaries between security domains as well as a way to cross the boundaries in a way where each domain retains their authority.
%The M-Machine~\citep{Dally1997Memo59} inspired capability machine in \citet{skorstengaard_reasoning_2017} uses enter-capabilities to achieve this.
On \trgcm{} we have CHERI-like sealed capabilities to achieve this~\cite{watson_cheri:_2015}.
Syntactically, sealed capabilities add two types of capabilities.
% seals
A set of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$ consists of a range of available seals $[\sigma_\var{base},\sigma_\var{end}]$ and the current seal $\sigma$, all represented by a natural number.
% sealed caps
A sealed capability $\sealed{\sigma,\vsc}$ consists of a sealable capability $\vsc$ and the seal $\sigma$ it has been sealed with.
Sealable capabilities $\vsc \in \SealableCaps$ are sets of seals or memory capabilities.

%%% Domains
The words on \trgcm{} are capabilities and data (represented by $\ints$).
We assume a finite set of register names $\RegName$ containing at least $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$, and we define register files as functions from register names to words.
We have complete memories mapping all addresses to words and memory segments mapping some addresses to words (i.e.\ partial functions).
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.\ an out-of-bounds memory access.
An executable configuration is a register file and memory pair.
